% KindOfNeat Resume Template -- modified from Leon Zaruvinsky under the MIT license
% Author: Nancy Zhang
% 
% There are two additionally defined types of subsection headers:
%
% \subsectiond{Arg 1}{Arg 2}
% Arg 1 is left aligned, Arg 2 is tabbed from Arg 1
%
% \subsectionp{Arg 1}{Arg 2}{Arg 3}
% Arg 1 is left aligned, Arg 2 is tabbed from Arg 1, and Arg 3 is right aligned
%
% \desc = description, aka paragraph
%
% % % % % % % % % % %
%
%

\documentclass{kindofneat}
\usepackage{hyphenat}
\usepackage{enumitem}

\begin{document}
\pagenumbering{gobble}
\name{Nancy (Ye) Zhang}
\info{Phone: 918-740-7732 | Email: \href{mailto:yez1@andrew.cmu.edu}{yez1@andrew.cmu.edu}
| US Greencard, CA citizen}


\noindent\rule{\textwidth}{1pt}

\large

\vspace*{2em}

\noindent Dear Hiring Committee,

\vspace*{1em}

I am writing to express my keen interest in the Firefox Core Engineering position posted on Handshake. I am currently a sophomore in computer science at Carnegie Mellon University. The open source background and collaborative spirit of Mozilla strongly appeals to my own passion for making the Web a better and more accessible place. I strongly believe that my teamwork abilities and quick learning will qualify me for this position.

\vspace*{0.5em}

I am a dedicated and responsible team player who uses collaboration to come up with innovative solutions to problems. In the Great Theoretical Ideas in Computer Science course at Carnegie Mellon, I worked tirelessly in a group of four students to complete our difficult problem sets each week. I used my leadership and time management skills to ensure that we were all on the same page and went to the appropriate office hours. Then, I directed our group in many brain storming sessions to construct a complete solution out of everyone's contributions. For example, we all had a separate idea of a reduction to an NP-complete problem, but I was able to synthesize the ideas into one overall reduction. My hefty experience in collaboration will prepare me for the team-based projects at Mozilla. 

\vspace*{0.5em}
I am very fast at learning new technologies and utilizing them in a meaningful way. For my Summer Undergraduate Research Fellowship, I had to quickly master MATLAB in order to collect and analyze the experimental data that I had collected. I studied the language and program at home and by the second week, I was able to fix the MATLAB program that outputted special graphs that the graduate student had not been able to complete. In addition, I also picked up soldering to fix the electronic set-up that controlled the mouse experiment since the wires and other small components often broke off. After I was done with it, the rig was sturdier and stayed together much longer than before. My adaptibility and self-motivation will allow me to thrive in Mozilla's future-focused, fast-paced environment. 
\vspace*{0.5em}

As a result of my teamwork and fast learning capabilities, I am confident that I will be able to play a key role in the core development of Firefox. For more information regarding my academic or extracurricular activities, please refer to my enclosed resume or contact me via phone at 918-740-7732, or email at yez1@andrew.cmu.edu. I greatly appreciate your time and consideration.

\vspace*{1em}
\noindent Sincerely,

\vspace*{2em}
\noindent Nancy Zhang

\end{document}

